### 2017-09-09 paper/evaluation.tex
Removed unnecessary comments
pass on eval

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.

%% However, avoiding
%% frequent context switches is another factor to consider.  For example,
%% assuming there are at least two CPUs available for execution, cost can
%% be cut in half if two tests in a large test suite dominate execution
%% time and these tests are assigned to different CPUs.

%% It is therefore important to
%% speedup regressing testing in open-source projects.\Comment{not only
%%   to huge projects as those from Google~\cite{google-tap,google-ci}
%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}

%% For the case
%% where cost is distributed more evenly across test cases, one expects
%% that speedups will be a function of the number of cores.
%% These contradictory forces, pushing number of tests and cost
%% of each test up and down, make prediction of effectiveness challenging.

\begin{figure}[h]
    \centering
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-long.pdf}
      \caption{\label{fig:longtcost}Long group.}
    \end{subfigure}\\
    \vspace{2ex}
    \begin{subfigure}{0.47\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results/testcost-medium.pdf}
      \caption{\label{fig:medtcost}Medium group.}
    \end{subfigure}
    \caption{\label{fig:time-distributions}Time distributions. X-axis
        denote projects appearing in arbitrary order.}%
\end{figure}

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
\longg{} group.  This project contains only 26 tests, 17 of which take
less than 0.5s to run, one of which takes nearly 3s to run, two of
which take nearly 11s to run, four of which takes on average 3m to run, and two of
which take $\sim$8m to run.  For this project, 98.4\% of the
execution cost is dominated by 20\% of the tests; without these
two costly tests this project would have been classified as
short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.}%
  \vspace{-3ex}
\end{figure}

Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, albeit having a wider inter-quartile range (middle
50\% projects in this group are less predictable), have a higher
median and much higher average number of test cases.  Furthermore, we
noted a strong positive correlation between running time and number of
test on projects in the \longg{} group.  Considering the \medg{}
group, the correlation between these two variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

@@

This experiment evaluates the impact of making a growing number of
CPUs for testing available to the build system.  For that reason, we
used a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tahr (64-bit version). This experiment uses configuration
spawning a growing number of JVMs in different CPUs.  We selected
subject \subjectScalability{} in this experiment as it represents the
case of a long-running test suite (see Table~\ref{tab:speedup}) with
test cases distributed across many test classes~--~194.  Note that a
\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
test class is the smallest unit that can be used to spawn a test job
on a JVM and that we have no control over which test classes will be
assigned to which JVM that the build system forks.
Figure~\ref{fig:scalability} shows the reduction in running times as
more CPUs contribute to the execution.
We ran this experiment for a growing number of cores 1, 3, ..., 39. 
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  \centering
  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
  \caption{\label{fig:scalability}Scalability.}
  \vspace{-1ex}
\end{wrapfigure}
The plot shows results up to 17 cores as it is clear the tendency.
We noticed that improvements are marginal after three cores, which is
the basic setup we used in other experiments.
This saturation is justified by the presence of a single test class,
\CodeIn{org.mapdb.WALTruncat}, containing 15 test cases that take over
two minutes to run.

\begin{center}
\vspace{1ex}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
      execution FC0 scales with additional cores but there is a bound
      on the speedup one can get related to how well the test suite is
      balanced across test classes.}
  \end{minipage}
}
\vspace{1ex}
\end{center}

@@

%% \begin{figure}[h!]
%% \centering
%% \resizebox{.48\textwidth}{!}{%
%% \begin{tabular}{lcrrrrr}
%% \toprule
%% \emph{Subject} & \emph{\# of tests} & \emph{\SeqClassParMeth{}} & \emph{\ParClassSeqMeth{}} & \emph{\ParClassParMeth{}} & \emph{\ForkSeq{}} & \emph{\ForkParMeth{}}\\%
%% \midrule%
%% Linkedin Pinot & 356 & - & - & - & - & -\\%
%% %% Jenkins CI Github Plugin & - & - & - & - & 0\% & -\\%
%% %% Kite SDK & - & - & - & - & - & -\\%
%% %% \Fix{!?} Apache Giraph & 327 & - & - & - & - & -\\%
%% %% OpenMRS Core & - & - & - & - & - & -\\%
%% %% Jenkins CI Docker Workflow Plugin & - & - & - & - & 0\% & -\\%
%% %% \Fix{Flaky} Apache Eagle & - & - & - & - & - & -\\%
%% %%Geotools & 7701 & - & - & - & - & -\\%
%% %%Kuromoji & 672 & - & - & - & - & -\\%
%% %%Atomix & 99 & - & - & - & - & -\\%
%% %%\Fix{Snazy OHC} & - & - & - & - & - & -\\%
%% %%\Fix{RoaringBitmap} & - & - & - & - & - & -\\%
%% \bottomrule%
%% \end{tabular}}
%% \caption{\Fix{Tabela de flakiness}}
%% \label{tab:rq6-flaky}
%% \end{figure}

@@

%% \Fix{Elaborate results from efficiency}

%% \Fix{Elaborate results from flakiness}

%% \Fix{highlight special cases}

>>>>

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.
%% However, avoiding
%% frequent context switches is another factor to consider.  For example,
%% assuming there are at least two CPUs available for execution, cost can
%% be cut in half if two tests in a large test suite dominate execution
%% time and these tests are assigned to different CPUs.
%% It is therefore important to
%% speedup regressing testing in open-source projects.\Comment{not only
%%   to huge projects as those from Google~\cite{google-tap,google-ci}
%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
%% For the case
%% where cost is distributed more evenly across test cases, one expects
%% that speedups will be a function of the number of cores.
%% These contradictory forces, pushing number of tests and cost
%% of each test up and down, make prediction of effectiveness challenging.

Figure~\ref{fig:time-distributions} shows the time distribution of
individual test cases per project (x-axis denote projects appearing in
arbitrary order).
We observed that the average median value of execution cost for a
test was relatively small (dashed horizontal red lines), namely 0.08s
for \medg{} projects and 0.16s for \longg{} projects.
The standard deviations associated with each distribution were
relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
projects within specific ranges of $\sigma$ values.}  We noted a small
number of cases of CPU monopolization.
For example, the highest value of $\sigma$ occurred in
\CodeIn{uber\_chaperone}, a project from the \longg{} group.
This project contains only 26 tests, 17 of which take less than 0.5s
to run, one of which takes nearly 3s to run, two of which take nearly
11s to run, four of which takes on average 3m to run, and two of which
take $\sim$8m to run.
For this project, 98.4\% of the execution cost is dominated by 20\% of
the tests; without these two costly tests this project would have been
classified as short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

\begin{figure}[t!]
  \centering
  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
  \caption{\label{fig:time-distributions}Time distributions per projects.}%
\end{figure}
\begin{figure}[t!]
  \centering
  \begin{subfigure}{0.15\textwidth}
    \centering
    \includegraphics[width=.85\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}Size of test suites.}
  \end{subfigure}
  ~
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=.95\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}Size versus running time of
      test suites.}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}Relating size and time.
  }%
\end{figure}
Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, albeit having a wider inter-quartile range (middle
50\% projects in this group are less predictable), have a higher
median and much higher average number of test cases.  Furthermore, we
noted a strong positive correlation between running time and number of
test on projects in the \longg{} group.  Considering the \medg{}
group, the correlation between these two variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

@@

This experiment evaluates the impact of making a growing number of
CPUs for testing available to the build system.  For that reason, we
used a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tahr (64-bit version). This experiment uses configuration
spawning a growing number of JVMs in different CPUs.  We selected
subject \subjectScalability{} in this experiment as it represents the
case of a long-running test suite (see Table~\ref{tab:speedup}) with
test cases distributed across many test classes~--~194.  Note that a
\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
test class is the smallest unit that can be used to spawn a test job
on a JVM and that we have no control over which test classes will be
assigned to which JVM that the build system forks.
Figure~\ref{fig:scalability} shows the reduction in running times as
more CPUs contribute to the execution.
We ran this experiment for a growing number of cores 1, 3, ..., 39. 
The plot shows results up to 17 cores as it is clear the tendency.
We noticed that improvements are marginal after three cores, which is
the basic setup we used in other experiments.
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  \centering
  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
  \caption{\label{fig:scalability}Scalability.}
\end{wrapfigure}
This saturation is justified by the presence of a single test class,
\CodeIn{org.mapdb.WALTruncat}, containing 15 test cases that take over
two minutes to run.

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupTwo{}:}~\emph{Results suggest that
      execution FC0 scales with additional cores but there is a bound
      on the speedup one can get related to how well the test suite is
      balanced across test classes.}
  \end{minipage}
}
\vspace{1ex}
\end{center}

@@

@@
